### 2015-04-26 evaluation.tex
various updates

\noindent
\textbf{Benchmarks}\xspace\xspace We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. To thoroughly test \whoop against the Linux driver APIs, we chose drivers from many different domains: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. We manually modeled the environment for all these drivers. This process required more than a month of work. We also focused on choosing non-trivial drivers (e.g. large number of entry points, deep nesting of entry point helper functions, complex use of locking, use of function pointers, etc).

@@

We can see that, in general, \whoop reports (many) more races than \corral. This is expected, though, as \whoop over-approximates the original driver for soundness. This means that if a race exists, \whoop will report it (assuming tool and model correctness). On the other hand, \corral performs bounded checking, which means that it will report a race only under pre-defined bounds. It is worthwhile to note that a common problem for \corral when analyzing drivers is loop coverage. To deal with this we enable the over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.

>>>>

\noindent
\textbf{Benchmarks}\xspace\xspace We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. To thoroughly test \whoop against the Linux driver APIs, we chose drivers from many different domains: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. Further, we focused on choosing non-trivial drivers (e.g. large number of entry points, deep nesting of entry point helper functions, complex use of locking, use of function pointers, etc). We manually modeled the environment for all these drivers, a process that required more than a month of work.

@@

We can see that, in general, \whoop reports (many) more races than \corral. This is expected because \whoop over-approximates the original driver for soundness: if a race exists, the tool will report it (assuming tool and model correctness), but \whoop can also report false races. On the other hand, \corral reports only real races, but does that under pre-defined bounds. It is worthwhile to note that a common problem for \corral (especially when analyzing drivers) is loop coverage. To deal with this we enable the over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.
